Optimal management of a stochastically varying population when policy adjustment is costly

### 2013-12-04 inst/doc/policycosts/policycosts.Rnw
source in scripts to Rnw manuscript

\begin{document}
%\SweaveOpts{concordance=TRUE, echo=FALSE}

@@

<<settings, echo=FALSE, warning=FALSE>>=
require(knitr)
opts_chunk$set(echo=FALSE, dev="pdf", cache=FALSE, warning=FALSE)
require(pdgControl)
require(reshape2)
require(ggplot2)
require(data.table)
require(plyr)
require(xtable)
load("writeup.rda")
theme_set(theme_bw())
@

>>>>

\begin{document}
%\SweaveOpts{concordance=TRUE, echo=FALSE}
<<settings, echo=FALSE, warning=FALSE>>=
require(knitr)
opts_chunk$set(echo=FALSE, dev="pdf", cache=FALSE, warning=FALSE)
require(pdgControl)
require(reshape2)
require(ggplot2)
require(data.table)
require(plyr)
require(xtable)
#load("writeup.rda")
theme_set(theme_bw())
@

<<maincode, echo=FALSE, warning=FALSE>>=
source("writeup.R")
@
<<errortable, echo=FALSE, warning=FALSE>>=
source("errors_table.R")
@

@@
